---
title: "<center> Assignment 9 <center>"
author: "<center> YUYU ZHANHG <center>"
date: "<center> 14/11/2020 <center>"
output:
  pdf_document: 
    fig_height: 4.25
    fig_width: 5
    latex_engine: xelatex
  html_document:
    df_print: paged
---

## 7.5.1

#### a.

```{r}
f <- function(x) 1/(5*sqrt(2*pi))* x^2 * exp(- (x - 2)^2 / 2)
integrate(f, -Inf, Inf)
## Monte Carlo approximation
nrep1 <- 1000
nrep2 <- 10000
nrep3 <- 50000
n <- 10000

i.n <- replicate(nrep1, {x <- rnorm(n, -1, 2); mean(f(x) / dnorm(x, -1, 2))})
mean(i.n)
sd(i.n)

i.c <- replicate(nrep1, {x <- rcauchy(n, -1, 2); mean(f(x) / dcauchy(x, -1, 2))})



mean(i.c)
sd(i.c)

```
#### b
I would like to use Gamma distribution as g(x) because we want to find out E($x^2$) and the estimator of $\mu=\frac{1}{n}\sum h(Z_i)$

#### c
```{r}
isAppr <- function(n, h, df, dg, rg, ...) {
  x <- rg(n, ...)
  mean( h(x) * df(x) / dg(x, ...) )
}

alpha <- 2
h <- function(x) 1/(5*sqrt(2*pi))* x^2 * exp(- (x - 2)^2 / 2)
beta <- 2
df <- function(x) dexp(x, rate = 1 / beta)

mySummary <- function(nrep, n, h, df, dg, rg) {
##    browser()
    sim <- replicate(nrep, isAppr(n, h, df, dg, rg))
    c(mean = mean(sim), sd = sd(sim))
}

sapply(1:6, 
       function(shp) {
           rg <- function(n) rgamma(n, shape = shp, scale = beta)
           dg <- function(x) dgamma(x, shape = shp, scale = beta)
           mySummary(1000, 1000, h, df, dg, rg)
       })

```
I just assume that g(x) is Gama distribution. and the result is more relaible than the standard normal distribution.

#### d



## 7.5.2

#### 1.Write down and implement an algorithm to sample the path of  S(t)

\[\frac{dS(t)}{S(t)}=\mu dt + \sigma dB(t)\]
Notice that the left hand side of this equation looks similar to the derivative of logS(t) . Applying Ito's Lemma to logS(t)  gives:
\[d(logS(t))=(logS(t))'\mu S(t)dt+(logS(t))'\sigma S(t)dB(t)
+ \frac{1}{2} (logS(t))''\sigma^2 S(t)^2dt\]
This becomes:\
\[d(logS(t))=\mu dt + \sigma d B(t)-\frac{1}{2}\sigma^2dt =(\mu -\frac{1}{2} \sigma^2)dt+\sigma dB(t)\]
This is an Ito drift-diffusion process. It is a standard Brownian motion with a drift term. Since the above formula is simply shorthand for an integral formula, we can write this as:\
\[log(S(t))-log(S(0))=(\mu -\frac{1}{2} \sigma^2)t+\sigma B(t)\]
Finally, taking the exponential of this equation gives:\
\[S(t)=S(0)exp((\mu -\frac{1}{2} \sigma^2)t+\sigma B(t))\]
This is the solution the stochastic differential equation


#### 2. Set $\sigma$ = 0.5 and T=1
\
```{r}
blackScholes <- function(strike, time, S0, rfrate, sigma) {
    crit <- (log(strike / S0) - (rfrate - sigma^2 / 2) * time)/ sigma / sqrt(time)
    S0 * pnorm(sigma * sqrt(time) - crit) -
      strike * exp(- rfrate * time) * pnorm(-crit)
}


Sa<- function(strike, time, S0, rfrate, sigma) {
    crit <- (log(strike / S0) - (rfrate - sigma^2 / 2) * time)/ sigma / sqrt(time)
    (1/12 )*S0*(13)/2-
      strike * exp(- rfrate * time) * pnorm(-crit)
}

Sg<- function(strike, time, S0, rfrate, sigma,n) {
   crit <- (log(strike / S0) - (rfrate - sigma^2 / 2) * time)/ sigma / sqrt(time)  
  (sqrt(factorial(12)))  -
        strike * exp(- rfrate * time) * pnorm(-crit)
}
nsim<-5000
strike<-1.1
S0 <-1 
time<-1
rfrate <- 0.05
sigma <- 0.5
## analytic solution
blackScholes(strike, time, S0, rfrate, sigma)

Sa(strike, time, S0, rfrate, sigma)
Sg(strike, time, S0, rfrate, sigma)
## Monte Carlo approximation
myApprox <- function(msim, strike, time, S0, rfrate, signma) {
    wt <- rnorm(nsim, sd = sqrt(time) * sigma)
    value <- mean(pmax(S0 * exp((rfrate - sigma^2 / 2) * time + wt) - strike, 0))
    exp(-rfrate * time) * value
}




mcAppr<-replicate(200, myApprox(nsim, strike, time, S0, rfrate, sigma))
sd(mcAppr)
mean(mcAppr)






```
By change the value of strike price , we see the larger K is , the smaller corrlation Pa and Pe with.

#### c

```{r}
myApprox <- function(msim, strike, time, S0, rfrate, signma) {
    wt <- rnorm(nsim, sd = sqrt(time) * sigma)
    value <- mean(pmax(S0 * exp((rfrate - sigma^2 / 2) * time + wt) - strike, 0))
    exp(-rfrate * time) * value
}

S0 <-1 
time<-1
rfrate <- 0.05
sigma <- 0.4

nsim<-5000
strike<-1.5
mcAppr<-replicate(200, myApprox(nsim, strike, time, S0, rfrate, sigma))
sd(mcAppr)
mean(mcAppr)


```
well it is obvious that the greater $\sigma$ is , the correlation coefficients get greater.

####d

```{r}
myApprox <- function(msim, strike, time, S0, rfrate, signma) {
    wt <- rnorm(nsim, sd = sqrt(time) * sigma)
    value <- mean(pmax(S0 * exp((rfrate - sigma^2 / 2) * time + wt) - strike, 0))
    exp(-rfrate * time) * value
}

S0 <-1 
time<-0.8
rfrate <- 0.05
sigma <- 0.5

nsim<-5000
strike<-1.5
mcAppr<-replicate(200, myApprox(nsim, strike, time, S0, rfrate, sigma))
sd(mcAppr)
mean(mcAppr)
```
It is shown that the greater T is , the correlation coefficients get greater.



